A Comparison of Graph Processing Systems

### 2020-08-29 documentation/paper/main.tex
preliminaries, more results, giraph and testingMethods reworked

\documentclass[conference,a4paper]{IEEEtran}

\usepackage[noadjust]{cite}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{textcomp}
\usepackage{pifont}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}

\usepackage{tabularx}
\def\tabularxcolumn#1{m{#1}} % vertical centering in tabularx cells
\newcolumntype{Y}{>{\centering\arraybackslash}X} % cell type Y for centered text with automatic line breaks
\newcommand*\rot{\rotatebox{90}} % rotates content 90deg ccw, mainly for table headers
\newcommand*\OK{\ding{51}} % a checkmark-style sign

@@

\author{\IEEEauthorblockN{Simon König}
\IEEEauthorblockA{(3344789)\\
st156571@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Leon Matzner}
\IEEEauthorblockA{(3315161)\\
@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Felix Rollbühler}
\IEEEauthorblockA{(3310069)\\
st154960@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Jakob Schmid}
\IEEEauthorblockA{(3341630)\\
@stud.uni-stuttgart.de}}

@@

\begin{abstract}
In this paper we will analyze and compare the graph frameworks Galois, Ligra, Polymer, Gemini and Giraph in their parformance. All the frameworks will be tested in shared memory and Galois, Gemini and Giraph are tested on a distributed cluster as well.
Furthermore we will give some insight on the complexity of writing custom applications based on these frameworks.
\end{abstract}

@@

\section{Introduction}
%\todo
In recent years graph sizes have increased significantly, thus performance and memory efficiency of the graph analysis applications is now more important than ever.

This paper makes the following contributions:
\begin{itemize}
  \item Comparison of some of the most widely used graph based calculation frameworks
  \item
  \item
  \item
\end{itemize}

\section{Overview of the framworks}
\subsection{Galois and Gluon}
\input{sections/overview/galois}

\subsection{Gemini}
\input{sections/overview/gemini}

\subsection{Giraph}
\input{sections/overview/giraph}

\subsection{Ligra}
\input{sections/overview/ligra}

\subsection{Polymer}
\input{sections/overview/polymer}

\section{And}
\input{sections/graphFormats}%hier oder supplementary data?

\section{Testing methods}
\input{sections/testingMethods}

\section{Results}
\input{sections/results/results}

@@

\section{Conclusion}
The conclusion goes here.

\section*{Acknowledgment}
We are using the graph frameworks Galois~\cite{Galois}, Ligra~\cite{Ligra}, Polymer~\cite{Polymer}, Gemini~\cite{Gemini} as well as Apache Giraph~\cite{Giraph}.

@@

\section*{Supplementary Data}\label{supplementaryData}
We have written a number of conversion tools and installation guides to help
users or developers with the use of the tested frameworks.

@@

% Generated by IEEEtran.bst, version: 1.12 (2007/01/11)
% Generated by IEEEtran.bst, version: 1.12 (2007/01/11)
% Generated by IEEEtran.bst, version: 1.12 (2007/01/11)
\begin{thebibliography}{1}
\providecommand{\url}[1]{#1}
\csname url@samestyle\endcsname
\providecommand{\newblock}{\relax}
\providecommand{\bibinfo}[2]{#2}
\providecommand{\BIBentrySTDinterwordspacing}{\spaceskip=0pt\relax}
\providecommand{\BIBentryALTinterwordstretchfactor}{4}
\providecommand{\BIBentryALTinterwordspacing}{\spaceskip=\fontdimen2\font plus
\BIBentryALTinterwordstretchfactor\fontdimen3\font minus
  \fontdimen4\font\relax}
\providecommand{\BIBforeignlanguage}[2]{{%
\expandafter\ifx\csname l@#1\endcsname\relax
\typeout{** WARNING: IEEEtran.bst: No hyphenation pattern has been}%
\typeout{** loaded for the language `#1'. Using the pattern for}%
\typeout{** the default language instead.}%
\else
\language=\csname l@#1\endcsname
\fi
#2}}
\providecommand{\BIBdecl}{\relax}
\BIBdecl

@@

@@

\bibitem{adjListFormat}
\BIBentryALTinterwordspacing
J.~Shun, G.~Blelloch, J.~Fineman, P.~Gibbons, A.~Kyrola, K.~Tangwonsan, and
  H.~V. Simhadri. (2020, Jun.) {Problem Based Benchmark Suite}. graphIO.html.
  [Online]. Available: \url{http://www.cs.cmu.edu/~pbbs/benchmarks/}
\BIBentrySTDinterwordspacing

\bibitem{Giraph}
\BIBentryALTinterwordspacing
A.~S. Foundation. (2020, Jun.) {Apache Giraph}. [Online]. Available:
  \url{https://giraph.apache.org}
\BIBentrySTDinterwordspacing

>>>>

\documentclass[a4paper]{IEEEtran}

\usepackage[noadjust]{cite}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{textcomp}
\usepackage{pifont}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amssymb}

\usepackage{tabularx}
\def\tabularxcolumn#1{m{#1}} % vertical centering in tabularx cells
\newcolumntype{Y}{>{\centering\arraybackslash}X} % cell type Y for centered text with automatic line breaks
\newcommand*\rot{\rotatebox{45}} % rotates content 90deg ccw, mainly for table headers
\newcommand*\OK{\ding{51}} % a checkmark-style sign

@@

\author{\IEEEauthorblockN{Simon König}
\IEEEauthorblockA{(3344789)
st156571@stud.uni-stuttgart.de}

\and

\IEEEauthorblockN{Leon Matzner}
\IEEEauthorblockA{(3315161)
st155698@stud.uni-stuttgart.de}

\and

\IEEEauthorblockN{Felix Rollbühler}
\IEEEauthorblockA{(3310069)
st154960@stud.uni-stuttgart.de}

\and

\IEEEauthorblockN{Jakob Schmid}
\IEEEauthorblockA{(3341630)
st157100@stud.uni-stuttgart.de}}

@@

\begin{abstract}
TODO
\end{abstract}

@@

\section*{TODOs}
\begin{itemize}
  \item Appendix für Setup Guides - md zu pdf
\end{itemize}

\section{Introduction}
% In recent years graph sizes have increased significantly [?] .
% Thus performance and memory efficiency of the graph analysis applications is now more important than ever.

% Many applications like

% Wachsende graphen,
% benötigt für folgende Applikationen,
% verwenden graph algorithmen,
% diese müssen schnell und verteilt laufen
% dafür wurden Frameworks entwickelt...

% und das noch schön formulieren

% We compare several non-uniform memory access (NUMA) aware systems in terms of their performance on three graph algorithms (PageRank, SSSP, BFS).
% The comparison is performed on both real world data sets and synthetic graphs.

% To provide a comparison to a non-NUMA aware system, Giraph\cite{Giraph} is included in the testing. Giraph itself has often been compared to other state of the art systems like Pregel or GraphX.

%One of the most famous is the (closed source) distributed graph processing system Pregel. Pregel and several open source versions of .
%This results in suboptimal performance, due to missing cache locality, because the Pregel like systems are written in an object oriented manner relying on pointer chasing mechanisms.

% To this end several non-uniform memory access (NUMA) aware systems were proposed like Polymer \cite{Polymer}, Galois \cite{Galois} or Ligra \cite{Ligra}.

This paper makes the following contributions:
\begin{itemize}
  \item Comparison of several state-of-the-art graph processing frameworks
  \item
  \item
  \item
\end{itemize}

\input{sections/preliminiaries}

\input{sections/overview/overview}

\input{sections/testingMethods}

\input{sections/results/results}

@@

\section{Conclusion}

\clearpage

\section*{Acknowledgments}
We are using the graph frameworks Galois~\cite{Galois}, Ligra~\cite{Ligra}, Polymer~\cite{Polymer}, Gemini~\cite{Gemini} as well as Apache Giraph~\cite{Giraph}.

@@

\appendices
\section{Installation Guides}\label{app:installationGuides}
The complete installation guides with steps on how to run the same algorithms we used is available in our repository\footnote{\url{https://github.com/SerenGTI/Forschungsprojekt/tree/master/documentation}}

In case of frameworks like Giraph, where for example no BFS algorithm is provided by the framework itself, the algorithm and a guide on how to include it in the framework can be found in the repository as well.

\section{Conversion Tool}\label{app:conversionTool}
In order to

We have written a number of conversion tools and installation guides to help
users or developers with the use of the tested frameworks.

@@

% Generated by IEEEtran.bst, version: 1.12 (2007/01/11)
\begin{thebibliography}{1}
\providecommand{\url}[1]{#1}
\csname url@samestyle\endcsname
\providecommand{\newblock}{\relax}
\providecommand{\bibinfo}[2]{#2}
\providecommand{\BIBentrySTDinterwordspacing}{\spaceskip=0pt\relax}
\providecommand{\BIBentryALTinterwordstretchfactor}{4}
\providecommand{\BIBentryALTinterwordspacing}{\spaceskip=\fontdimen2\font plus
\BIBentryALTinterwordstretchfactor\fontdimen3\font minus
  \fontdimen4\font\relax}
\providecommand{\BIBforeignlanguage}[2]{{%
\expandafter\ifx\csname l@#1\endcsname\relax
\typeout{** WARNING: IEEEtran.bst: No hyphenation pattern has been}%
\typeout{** loaded for the language `#1'. Using the pattern for}%
\typeout{** the default language instead.}%
\else
\language=\csname l@#1\endcsname
\fi
#2}}
\providecommand{\BIBdecl}{\relax}
\BIBdecl

\bibitem{bsp}
\BIBentryALTinterwordspacing
L.~G. Valiant, ``A bridging model for parallel computation,'' \emph{Commun.
  ACM}, vol.~33, no.~8, p. 103–111, Aug. 1990. [Online]. Available:
  \url{https://doi.org/10.1145/79173.79181}
\BIBentrySTDinterwordspacing

@@

\bibitem{Giraph}
\BIBentryALTinterwordspacing
{Apache Software Foundation}. (2020, Jun.) {Apache Giraph}. [Online].
  Available: \url{https://giraph.apache.org}
\BIBentrySTDinterwordspacing

@@

\bibitem{pbbs}
\BIBentryALTinterwordspacing
J.~Shun, G.~Blelloch, J.~Fineman, P.~Gibbons, A.~Kyrola, K.~Tangwonsan, and
  H.~V. Simhadri. (2020, Aug.) {Problem Based Benchmark Suite }. [Online].
  Available: \url{http://www.cs.cmu.edu/~pbbs/}
\BIBentrySTDinterwordspacing

### 2020-08-29 documentation/paper/sections/graphFormats.tex
preliminaries, more results, giraph and testingMethods reworked

\subsection{An Overview of Important Graph Formats}
Since every frameworks uses different graph input formats, we supply a conversion tool capable of translating from EdgeList to the required formats.
Data Sets retreived from KONECT can be directly read and translated.

>>>>

\subsection{Important Graph Formats}
Since every frameworks uses different graph input formats, we supply a conversion tool capable of translating from EdgeList to the required formats.
Data Sets retreived from KONECT can be directly read and translated.
